---
title: "p8105_hw1_yy3421"
author: "Yilei Yang"
date: "2023-09-20"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1:

```{r}
library(moderndive)
data("early_january_weather")
early_january_weather
```

Early January Weather Dataset:

This dataset consists of 15 variables, including origin, year, month, day, hour, temperature, dew point, humidity, wind direction, wind speed, wind gust, precipitation, visibility, and hour time.

The dataset consists of `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature is `r mean(early_january_weather$temp)`.

```{r, scatterplot}
library(tidyverse)
ggplot(
  early_january_weather, 
  aes(
    x = time_hour, 
    y = temp,
    color = humid
    )
  )+ geom_point()
ggsave("scatterplot.pdf")
```

# Problem 2:

```{r}
problem2_df = tibble(
  sample_data = rnorm(10),
  vec_log = sample_data > 0,
  vec_char = letters[1:10],
  vec_factor = factor(c("I", "II", "III", "I", "II", "I", "III", "II", "I", "III")),
)
```

```{r, mean calculation}
library(tidyverse)
sample_data_mean = mean(pull(problem2_df, sample_data))
vec_log_mean = mean(pull(problem2_df, vec_log))
vec_char_mean = mean(pull(problem2_df, vec_char))
vec_factor_mean = mean(pull(problem2_df, vec_factor))

```

The means of the first two columns, sample_data and vec_log, works. However, vec_char and vec_factor don't work for mean calculation.

