---
title: "p8105_hw1_yy3421"
author: "Yilei Yang"
date: "2023-09-20"
output: github_document
---

# Problem 1:
Load moderndive library:

```{r}
library(moderndive)
data("early_january_weather")
early_january_weather
```

Early January Weather Dataset:

This dataset consists of 15 variables. Some of the important weather variables include temperature, dew point, humidity, wind direction, wind speed, wind gust, precipitation, and visibility.

The dataset consists of `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature is `r mean(early_january_weather$temp)` degree Celsius.

```{r, scatterplot}
library(tidyverse)
ggplot(
  early_january_weather, 
  aes(
    x = time_hour, 
    y = temp,
    color = humid
    )
  )+ geom_point()
```

Looking at the scatterplot, there is a overall increasing trend of the temperature until Jan 14th and a decreasing trend after Jan 14th. The humidity is generally low before Jan 11th and after Jan 15th. Between Jan 11th and 15th, the humidity is high with an approxiate average of 100.

```{r}
ggsave("scatterplot.pdf")
```

# Problem 2:

```{r}
problem2_df = tibble(
  sample_data = rnorm(10),
  vec_log = sample_data > 0,
  vec_char = letters[1:10],
  vec_factor = factor(c("Level I", "Level II", "Level III", "Level I", "Level II", "Level I", "Level III", "Level II", "Level I", "Level III")),
)
problem2_df
```

Calculating mean values:

```{r, mean calculation}
library(tidyverse)
sample_data_mean = mean(pull(problem2_df, sample_data))
vec_log_mean = mean(pull(problem2_df, vec_log))
vec_char_mean = mean(pull(problem2_df, vec_char))
vec_factor_mean = mean(pull(problem2_df, vec_factor))

```

The means of the first two columns, sample_data and vec_log, works. However, vec_char and vec_factor don't work for mean calculation.

```{r, testing as.numeric}
test_log = as.numeric(problem2_df$vec_log)
test_char = as.numeric(problem2_df$vec_char)
test_factor = as.numeric(problem2_df$vec_factor)
```

The message "Warning: NAs introduced by coercion" is displayed becuase the character column, containing letters, cannot be converted to numerical values.This explains the previous result of failed mean calculation of the character column. Non-numerical values cannot be used to calculate mean values. However, for the factor value, the original factor levels are factor vectors with numerical expressions. Before using the as.numeric function, mean value cannot be calculated for factor vectors. After using the as.numeric function, it is converted into numerical values.


