---
title: "p8105_hw1_yy3421"
author: "Yilei Yang"
date: "2023-09-20"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1:
Load moderndive library:

```{r}
library(moderndive)
data("early_january_weather")
early_january_weather
```

Early January Weather Dataset:

This dataset consists of 15 variables, including origin, year, month, day, hour, temperature, dew point, humidity, wind direction, wind speed, wind gust, precipitation, visibility, and hour time.

The dataset consists of `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature is `r mean(early_january_weather$temp)`.

```{r, scatterplot}
library(tidyverse)
ggplot(
  early_january_weather, 
  aes(
    x = time_hour, 
    y = temp,
    color = humid
    )
  )+ geom_point()
ggsave("scatterplot.pdf")
```

# Problem 2:

```{r}
problem2_df = tibble(
  sample_data = rnorm(10),
  vec_log = sample_data > 0,
  vec_char = letters[1:10],
  vec_factor = factor(c("Level I", "Level II", "Level III", "Level I", "Level II", "Level I", "Level III", "Level II", "Level I", "Level III")),
)
```

```{r, mean calculation}
library(tidyverse)
sample_data_mean = mean(pull(problem2_df, sample_data))
vec_log_mean = mean(pull(problem2_df, vec_log))
vec_char_mean = mean(pull(problem2_df, vec_char))
vec_factor_mean = mean(pull(problem2_df, vec_factor))

```

The means of the first two columns, sample_data and vec_log, works. However, vec_char and vec_factor don't work for mean calculation.

```{r, testing as.numeric}
test_log = as.numeric(problem2_df$vec_log)
test_char = as.numeric(problem2_df$vec_char)
test_factor = as.numeric(problem2_df$vec_factor)
```

The message "Warning: NAs introduced by coercion" is displayed becuase the character column, containing letters, cannot be converted to numerical values.This explains the previous result of failed mean calculation of the character column. Non-numerical values cannot be used to calculate mean values. However, for the factor value, the original factor levels are factor vectors with numerical expressions. Before using the as.numeric function, mean value cannot be calculated for factor vectors. After using the as.numeric function, it is converted into numerical values.


